---
title: "DivSup: Full-Sample Analyses"
output: html_document
---

```{r, include = F}
## Load packages
library(tidyverse)
library(broom)
library(here)
library(scales)
library(kableExtra)
library(oddsratio)
library(modelsummary)
`%+%` <- paste0


## Load data
clean_data <- readRDS(here("Data", "Clean Data.rds"))


## Set global variables
# Vector of researcher characteristics
researcher_characteristics <- c(
  "age",
  "gender_factor",
  "race_ethnicity_recoded",
  "discipline_factor",
  "institution_type",
  "job_title",
  "research_time",
  "research_funding",
  "years_experience",
  "mentor_undergrad",
  "mentor_postbac",
  "mentor_masters",
  "mentor_doctoral",
  "mentor_postdoc",
  "mentor_ecr"
)


## Functions
# Return mean and SD for numeric variables
mean_sd <- function(x) {
  
  clean_data %>%
    summarize(
      mean = mean(get(x), na.rm = T),
      sd = sd(get(x), na.rm = T)
    ) %>%
    kable() %>%
    kable_styling() %>%
    return()
  
}

# Return n's and percents for categorical variables, dropping NA's
n_pct <- function(x) {
  
  clean_data %>%
    count(get(x)) %>%
    rename({{x}} := `get(x)`) %>%
    drop_na() %>%
    mutate(pct = percent(n / sum(n), .1)) %>%
    kable() %>%
    kable_styling() %>%
    return()
  
}

# CI's using Wilson's score method (see Newcombe 1998)
prop_ci <- Vectorize(function(x, n, side = c("lower", "upper")) {
  
  test_output <- prop.test(x = x, n = n)
  
  if(side == "lower") {
    
    return(test_output$conf.int[1])
    
  } else if(side == "upper") {
    
    return(test_output$conf.int[2])
    
  }
  
})

# Chi-square test output
print_chisq <- function(chisq.test) {
  
  statistic <- chisq.test$statistic %>%
    round(3)
  
  df <- chisq.test$parameter
  
  p <- chisq.test$p.value %>%
    round(3)
  
  print("X2 (" %+% df %+% ") = " %+% statistic %+% ", p = " %+% p)
  
}
```

## Descriptive Statistics

Means and standard deviations for continuous variables.

```{r}
mean_sd("age")
mean_sd("years_experience")
mean_sd("research_time")
mean_sd("research_funding")
```

Counts and percents for categorical variables, excluding missing values. Because not all participants responded to all questions, the overall N's will be different for some of these tables. Also note that some variables are recoded for analysis (more on that below, as it comes up).

```{r}
n_pct("gender")
n_pct("race_ethnicity")
n_pct("discipline")
n_pct("institution_type")
n_pct("job_title")
n_pct("mentor_undergrad")
n_pct("mentor_postbac")
n_pct("mentor_masters")
n_pct("mentor_doctoral")
n_pct("mentor_postdoc")
n_pct("mentor_ecr")
n_pct("div_sup_applied")
n_pct("div_sup_granted")
```

## Application by Researcher Characteristics

These first tables show the *bivariate models* - i.e., models that look at each IV in isolation, without controlling for other IVs. For models predicting application, race/ethnicity was recoded such that the categories AI/AN, NH/PI, multiple, and other were collapsed into "other".

```{r, results = "asis"}
# Bivariate models
for(x in researcher_characteristics) {
  
  model <- glm(
    data = clean_data,
    formula = as.formula("div_sup_applied ~ " %+% x),
    family = "binomial"
  )
  
  model %>%
    summary() %>%
    coef() %>%
    kable() %>%
    kable_styling()
    
  or <- or_glm(clean_data, model, incr = list(
    age = 10,
    research_time = 10,
    research_funding = 10,
    years_experience = 10
  ))
  
  or %>%
    kable() %>%
    kable_styling() %>%
    print()
  
}
```

This table includes results for the combined model.

```{r}
# Combined model
combined_model <- glm(
  data = clean_data,
  formula = as.formula("div_sup_applied ~ " %+% paste0(researcher_characteristics, collapse = " + ")),
  family = "binomial"
)

combined_model %>%
  summary() %>%
  coef() %>%
  kable() %>%
  kable_styling()

or <- or_glm(clean_data, combined_model, incr = list(
  age = 10,
  research_time = 10,
  research_funding = 10,
  years_experience = 10
))
  
or %>%
  kable() %>%
  kable_styling()
```

## Success by Researcher Characteristics

Same as above - this section is the bivariate models. Because the sample size for these analyses is smaller (limited to only respondents who applied for a DS), some new categorical variables had to be recoded (to prevent categories whose n's were too small to model). In addition to recoding race (as above), gender was recoded to make TGD (n = 4) NA (i.e., drop these respondents), discipline was recoded to make social psychology (n = 11) NA, and institution was recoded to make small college (n = 10) NA.

```{r, results = "asis"}
data_success <- clean_data %>%
  drop_na(div_sup_granted) %>%
  mutate(
    gender_factor = na_if(gender_factor, "TGD"),
    discipline_factor = na_if(discipline_factor, "Social Psychology"),
    institution_type = na_if(institution_type, "Small College")
  )

# Bivariate models
for(x in researcher_characteristics) {
  
  model <- glm(
    data = data_success,
    formula = as.formula("div_sup_granted ~ " %+% x),
    family = "binomial"
  )
  
  model %>%
    summary() %>%
    coef() %>%
    kable() %>%
    kable_styling()
  
  or <- or_glm(data_success, model, incr = list(
    age = 10,
    research_time = 10,
    research_funding = 10,
    years_experience = 10
  ))
  
  or %>%
    kable() %>%
    kable_styling() %>%
    print()
  
}
```

And the combined model: 

```{r}
# Combined model
combined_model <- glm(
  data = data_success,
  formula = as.formula("div_sup_granted ~ " %+% paste0(researcher_characteristics, collapse = " + ")),
  family = "binomial"
)

combined_model %>%
  summary() %>%
  coef() %>%
  kable() %>%
  kable_styling()

or <- or_glm(data_success, combined_model, incr = list(
  age = 10,
  research_time = 10,
  research_funding = 10,
  years_experience = 10
))
  
or %>%
  kable() %>%
  kable_styling()
```

## Barriers

```{r}
barrier_summary_data <- clean_data %>%
  count(top_barrier) %>%
  drop_na() %>%
  mutate(
    top_barrier = fct_reorder(top_barrier, n),
    prop = n / sum(n),
    lower = prop_ci(n, sum(n), "lower"),
    upper = prop_ci(n, sum(n), "upper")
  )

barrier_summary_data %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling()

barrier_summary_data %>%
  ggplot(aes(top_barrier, prop)) +
  geom_col() +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5) +
  scale_x_discrete(name = NULL) +
  scale_y_continuous(name = NULL, labels = percent) +
  coord_flip() +
  theme_classic()
```
